quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-02 paper-quollr.Rmd
Updated Figure 3

hex_grid_poly_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.2, size = 0.5, color = clr_choice) + 
  interior_annotation("a", cex = 3) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

The result is a `tibble` of the scaled $2\text{-}D$ embedding with an additional `h` column, indicating the hexagonal bin to which each point belongs. 
  ?

@@

>>>>

hex_grid_poly_scurve <- ggplot(
  data = hex_grid_with_counts_scurve, 
  aes(x = x, y = y)) +
  geom_polygon(color = "grey70", 
               aes(group = h), 
               fill = "#ffffff") +
  geom_point(data = scurve_umap_scaled, 
             aes(x = emb1, y = emb2), 
             alpha = 0.8, size = 0.5, color = clr_choice) + 
  interior_annotation("a", cex = 3) +
  xlim(sc_xlims) +
  ylim(sc_ylims)

@@

The result is a `tibble` of the scaled $2\text{-}D$ embedding with an additional `h` column, indicating the hexagonal bin to which each point belongs.

@@

After assiging data to the hexagons,
